Think deep for reef resilience

### 2025-08-12 paper/paper_draft.qmd
Remove redundant and repetitious mention of reef outlines
Adjust reef definition text for flow

The spatial extent of the GBR reefs represented in this investigation follows the reef
definitions available via the Great Barrier Reef Marine Park Authority (GBRMPA)
[@GBRMPA2022]. An indicative map of the GBR marine park including the Marine Park management
areas [@GBRMPA2007] and the corresponding bioregion for each reef is shown in
(@fig-region-map; [@GBRMPA2024]). This investigation adopts the GBR reef outlines as
published by GBRMPA [-@GBRMPA2022], which defines 3806 reefs across the GBR.

Depth characteristics for each reef were extracted using 10m resolution bathymetry data made
available in GBRMPA [-@GBRMPA2020]. For each reef, bathymetry data were spatially matched
with the 3806 reef outlines through geometric intersection analysis. Depth values within
each reef polygon were summarized using zonal statistics to calculate minimum, mean, median,
maximum, and standard deviation of depth values. All depth values were converted to positive
values (depths below sea level). The median depth was used to provide an indicative depth
value for each reef. Code, and the resulting depth estimates, are available at **\[cite
Canonical Reefs repo\]**.

While data adopted for the given assessment are said to be accurate up to 15m from Mean Sea
Level [@GBRMPA2020], there are many sources of uncertainty in the depth estimates used for
this study. These are outlined further in the Discussion. Notably, the adopted depth
estimates were derived from bathymetries based on satellite imagery. Available data can be
limited in their alignment with the established GBRMPA reef outlines used to characterise
reef locations and their areal extent. Quality control flags were assigned to identify
potential data limitations: reefs with no overlapping bathymetry data, reefs with minimum
depth values above sea level (indicating potential data artifacts), and reefs where
bathymetry pixels covered less than 5% of the reef polygon area. This removed 842 reefs, or
22%, from the initial set of 3806 reefs. Furthermore, reefs that are not associated with
GBRMPA management areas [@GBRMPA2007] or reefal bioregions [@GBRMPA2024] were also removed
from the investigation. Bioregions which contained fewer than three reefs were also
excluded. As a result, 1377 reefs were excluded (36%), leaving a total of 2429 remaining for
the purpose of this investigation.

>>>>

The spatial extent of the GBR reefs represented in this investigation follows the reef
definitions available via the Great Barrier Reef Marine Park Authority (GBRMPA)
[@GBRMPA2022]. The reef definitions define 3806 reefs across the GBR. An indicative map of
the GBR marine park including the Marine Park management areas [@GBRMPA2007] and the
corresponding bioregion for each reef is shown in (@fig-region-map; [@GBRMPA2024]).

Depth characteristics for each reef were extracted using 10m resolution bathymetry data made
available in GBRMPA [-@GBRMPA2020]. For each reef, bathymetry data were spatially matched
with the 3806 reef outlines through geometric intersection analysis. Depth values within
each reef polygon were summarized using zonal statistics. All depth values were converted to
positive values (depths below sea level). The median depth was used to provide an indicative
depth value for each reef. Code, and the resulting depth estimates, are available at
**\[cite Canonical Reefs repo\]**.

While the bathymetry data adopted for the given assessment are said to be accurate up to 15m
from Mean Sea Level [@GBRMPA2020], there are many sources of uncertainty in the depth
estimates used for this study. These are outlined further in the Discussion. Notably, the
adopted depth estimates were derived from bathymetries based on satellite imagery. The
bathymetry data can be limited in their alignment with the established GBRMPA reef outlines
used to characterise reef locations and their areal extent. A Quality Assessment and Control
process identified reefs with potential data limitations: reefs with no overlapping
bathymetry data, reefs with minimum depth values above sea level (indicating potential data
artifacts), and reefs where bathymetry pixels covered less than 5% of the reef polygon area.
This process removed 842 reefs, or 22%, from the initial set of 3806 reefs. Furthermore,
reefs that are not associated with GBRMPA management areas [@GBRMPA2007] or reefal
bioregions [@GBRMPA2024] were also removed from the investigation. Bioregions which
contained fewer than three reefs were also excluded. As a result, 1377 reefs were excluded
(36%), leaving a total of 2429 remaining for the purpose of this investigation.
